---
title: POL 478H1 F
subtitle: Intro to R
author: "Olga Chyzh [www.olgachyzh.com]"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
exclude: true
editor_options: 
  chunk_output_type: console
---
```{r  setup, message=FALSE, warning=FALSE, include=FALSE}
options(
  htmltools.dir.version = FALSE, # for blogdown
  width = 80,
  tibble.width = 80
)

knitr::opts_chunk$set(
  fig.align = "center",  warning=FALSE, message=FALSE
)

```



## Outline

- Input data

- Look at data

- Extract pieces

- Basic graphing in `ggplot2`

---
## Course Data

- Many commands/features in R are a part of a specific package.

- You must install and load the package in order to use these commands/features.

- We have an R package for this class. To install/update, copy and paste the following code into your RStudio source editor and run.

```{r}
library(devtools)
devtools::install_github("ochyzh/classdata")
```

- To load the package (at the beginning of each R session if you plan to use it):

```{r}
library(classdata)
```

---
#Getting Help Within R

If you want to learn about a specific command:
```{r, eval=F}
?command

help("command")

help.search("command")

??command
```


---

## R Reference Card

- http://cran.r-project.org/doc/contrib/Short-refcard.pdf

- Save/print it to reference as you work.

---

## Your Turn (5 min)

- Install the package `classdata` on your computer

- Load the package into your current R session:

```{r}
library(classdata)
```

- Look at the R help for the dataset  `terr_attacks`

- What happens if you just type in the name of the dataset?

---
## Exploring Objects

For any R object `x`, we can use any of the following:

- `x`

- `head(x)`

- `summary(x)`

- `str(x)`

- `dim(x)`

Try these commands on the `terr_attacks` data.

---
## `str` is for *structure*

```{r}
data(terr_attacks)
str(terr_attacks)
```

---
## Extract Parts of an Object

- `x$variable`

- `x[,"variable"]`

- `x[rows, columns]`

- `x$variable[rows]`

`rows` and `columns` are vectors or indices.

Try these commands on the `terr_attacks` data.

---
## Your Turn

- Look at the first 10 rows of the `terr_attacks` data

- Why are some values coded as `NA`? Look at the help for `NA`.


